ROV report

### 2020-03-21 analysis/reports/rov.Rmd
run with fia short

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(dat == "portal_plants") %>% 
    mutate(binned_nparts = as.factor(ceiling(log_nparts/10)))

all_diffs <- read.csv(here::here("all_diffs.csv"), stringsAsFactors = F)

all_diffs <- all_diffs %>%
  select(-X, -source)

>>>>

dis <- list.files(here::here("analysis", "results"), pattern = "all_di")
all_di <- lapply(dis, FUN = function(di_df) return(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F)))
all_di <- bind_rows(all_di)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>% 
    mutate(binned_nparts = as.factor(ceiling(log_nparts/10)))

diffs <- list.files(here::here("analysis", "results"), pattern = "diff_")
all_diffs <- lapply(diffs, FUN = function(di_df) return(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F)))
all_diffs <- bind_rows(all_diffs)

all_diffs <- all_diffs %>%
  select(-source)
